Judging domestic cooking ability: repeated incomplete rank observations

### 2025-03-03 inst/cook_repeated.Rmd
consistentify "time to process" information
bugfix

To cite the `hyper2` package in publications, please use @hankin2017_rmd;
takes about five minutes without cache.  Suppose there are five people
in a family.  Each day for five days, one person cooks a meal.  After
the fifth day, each person considers the four meals cooked by other
family members, and puts them in order of preference.  This process is
repeated and here I consider how to interpret such data.

@@

```{r lookatfirstrow}
(day1 <- cooking_table[1,])
H_row1 <- rank_likelihood(day1[day1>0])
```

@@

for(i in seq_len(nrow(cooking_table))){  # iterate over rows
jj <- cooking_table[i,] 
    H <- H + rank_likelihood(jj[jj>0])
}
H
```

@@

We can do slightly better, and test a more general hypothesis,
specifically that the girls systematically vote other girls higher,
and boys systematically vote boys higher, than warranted.  To test
this hypothesis, we posit two reified entities, `girl` and `boy`.
Entity `girl` helps a girl when another girl is voting for her, and
entity `boy` helps a boy when another boy is voting for him.

```{r girlsvotinggirls,cache=TRUE}
cooking_table <-
	as.matrix(read.table("cooking_weekly.txt", header=TRUE))
cooking_table <- cooking_table[rowSums(cooking_table==0)==1,]
boys <-c("robin","zac")
girls <- c("lesley","alice","annabel")
cooks <- colnames(cooking_table)
P <- hyper2()
P0 <- hyper2()
for(i in seq_len(nrow(cooking_table))){  # iterate over rows
    x <- cooking_table[i,] 
	if(sum(x==0)>1){break}
    names(x) <- cooks
	if(names(x[x==0]) %in% boys){  # if the voter is a boy
		x <- x[x>0]  # remove the voter
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% boys], chameleon="boy")
	} else if (names(x[x==0]) %in% girls){ # voter a girl
		x <- x[x>0]
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% girls], chameleon="girl")
	} else {
		stop()
	}
    P <- P + Pjj
}
mP <- maxp(P)
```

```{r plotapie}
mP
pie(mP)
```

Now test whether the girls preferentially vote:

```{r girlspref, cache=TRUE}
specificp.gt.test(P,"girl",0)
```

>>>>

<font size="1"> (takes about five minutes to run without cache)
</font>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  Suppose there are five people in a family.  Each day
for five days, one person cooks a meal.  After the fifth day, each
person considers the four meals cooked by other family members, and
puts them in order of preference.  This process is repeated and here I
consider how to interpret such data.

@@

```{r lookatfirstrow}
(day1 <- cooking_table[1,])
(H_row1 <- suppfun(names(sort(day1[day1 > 0]))))
```

@@

for(i in seq_len(nrow(cooking_table))){  # iterate over rows
jj <- cooking_table[i,] 
    H <- H + suppfun(sort(jj[jj > 0]))
}
H
```

@@

We can do slightly better, and test a more general hypothesis,
specifically that the girls systematically vote other girls higher,
and boys systematically vote boys higher, than warranted.  To test
this hypothesis, we either posit two reified entities, `girl` and `boy`.
Entity `girl` helps a girl when another girl is voting for her, and
entity `boy` helps a boy when another boy is voting for him.

Or we use multipliers and `hyper3` idiom (not yet done)
